---
title: "p8130_hw6_rw2844"
author: "Renjie Wei"
date: "11/30/2020"
output: 
  pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(cowplot)
library(patchwork)
library(modelr)
knitr::opts_chunk$set(
  echo = F,
  out.width = "100%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(2844)
```

# Problem 1


1. Create a correlation matrix

```{r read_patsatisfaction}
patsat_df = 
  read_csv("./data/PatSatisfaction.csv") %>% janitor::clean_names() %>% mutate(satisfaction = safisfaction) %>% select(satisfaction, everything(),-safisfaction)

patsat_df %>% cor() %>% corrplot::corrplot(type = "upper", order = "hclust", tl.col = "black", tl.srt = 45)
```

It seems that each predictor has a negative correlation with the outcome of interest.




2. Fit a multiple regression model.

```{r patsat_reg}
patsat_reg =
  lm(satisfaction ~ age + severity + anxiety, data = patsat_df)

null_reg = 
  lm(satisfaction ~ 1, data = patsat_df)
```



Let's set up the test hypotheses:

$H_0~:~\beta_i = 0,~i = 1,2,3$ 

$H_1 : at~least~one~of~the~coefficient~is~not~equal~to~0$

And our model to be test is:
$$Model_{test}:~Statisfaction=`r str_c(patsat_reg$coefficients %>% round(2),c("",patsat_reg$terms %>% attr("term.labels")),sep=" ") %>% paste(collapse = "")`$$

We can test this model against the model only with intercept:

$$Model_{null}:~Statisfaction=`r str_c(null_reg$coefficients %>% round(2),c("",null_reg$terms %>% attr("term.labels")),sep=" ") %>% paste(collapse = "")`$$

And we do the ANOVA test:

The F statistic is calculated by:
$$F_{stat} = \frac{MSR}{MSE} \sim F_{p,~n-p-1},~where~p=3,~n=46$$
```{r patsat_anova}
anova(null_reg, patsat_reg)
```

**Decision Rules:**
$Reject ~ H_0 ~ if ~ F_{stat}>F_{1-\alpha;~p,~n-p-1}$

In our situation, $F_{stat} = 30.1>F_{0.95;~3,~42}=`r qf(0.95,3,42)`$

So, we reject the null hypothesis with 95% confidence and conclude that at least one coefficient is not equal to zero.




3. Show the regression results for all estimated slope coefficients with 95% CIs.

```{r patsat_ci}
patsat_ci = 
  tibble(
    broom::tidy(patsat_reg),
    as_tibble(confint(patsat_reg))
  ) %>% 
  select(term, estimate, "2.5 %", "97.5 %")

patsat_ci %>% 
  knitr::kable(digits = 3)
```

**Interpretation:**

The 95% CI for severity of illness is $(-1.435,~0.551)$, that means at 95% confidence level, the mean 
change of patient satisfaction given all the same except for severity of illness per unit is between $(-1.435,~0.551)$, noticing that 0 is in this interval.




4. Obtain an interval estimate for a new patient’s satisfaction with Age=35, Severity=42, and Anxiety=2.1.

The 95% PI for this new patient is :
```{r patsat_int_est}
predict(
  patsat_reg,
  tibble(age=35, severity=42, anxiety=2.1),
  interval = "prediction"
  ) %>% 
  as_tibble() %>% 
  select(lwr,upr) %>% 
  knitr::kable(digits = 3)
```

**Interpretation:**

This means at 95% confidence level, the true estimate of patient satisfaction is between $(50.062, 93.304)$.




5. 
  a) Test whether ‘anxiety level’ can be dropped from the regression model, given the other two covariates are retained.
  
  
First, we set up the hypotheses:

$H_0~:~\beta_{anxiety} = 0$

$H_1~:~\beta_{anxiety} \ne 0$

And we conduct the ANOVA test:

$$F_{stat} = \frac{MSR(X3|X1X2)}{MSE(X1X2X3)} \sim F_{df_L - df_S,df_L},~where~df_L =43 ,~df_S =42 $$

```{r patsat_drop}
noanxi_reg = 
   lm(satisfaction ~ .-anxiety, data = patsat_df)

anova(noanxi_reg, patsat_reg)

```

**Decision Rules:**
$Reject ~ H_0 ~ if ~ F_{stat}>F_{1-\alpha;df_L - df_S,df_L}$

In our situation, $F_{stat} = 3.6<F_{0.95;~1,~42}=`r qf(0.95,1,42)`$

So, we cannot reject the null hypothesis with 95% confidence and conclude that ‘anxiety level’ can be dropped from the regression model.


  b) How are R2/R2-adjusted impacted
  
```{r rsq_comp}
rsq_comp = 
  tibble(
    Model = c("With Anxiety","Without Anxiety"),
    R_square = c(summary(patsat_reg)$r.square, summary(noanxi_reg)$r.square),
    Adjusted_R_square = c(summary(patsat_reg)$adj.r.square, summary(noanxi_reg)$adj.r.square)
  )

rsq_comp %>% knitr::kable(digits = 3)
```

We can see that the R square and Adjusted R square are higher in model with anxiety level.





# Problem 2





1. Crude association between BMI and serum estradiol

a) Scatter plot with regression line.

```{r estra_scat}
estradl_df  =
  read_csv("data/ESTRADL.csv") %>%
  janitor::clean_names() %>%
  mutate(ethnic =case_when(ethnic == 1 ~ "African American", ethnic == 0 ~ "Caucasian"),
         ethnic = as.factor(ethnic))


estradl_df %>% 
  ggplot(aes(x = bmi, y = estradl)) +
  geom_point() +
  stat_smooth(method = "lm", se = F) +
  labs(
    title = "Regress Estradiol on BMI",
    x = "BMI",
    y = "Estradiol level"
  )
```

**Comments:**

As the plot shown above, the regression line has a very small slope, and the slope is negative. And there are some outliers when BMI is low.


b) Regression output

```{r estradl_reg_bmi}
bmi_reg = 
  estradl_df %>%
  lm(estradl ~ bmi, data = .)

bmi_reg %>% broom::tidy() %>% knitr::kable(digits = 3)
```

**Comments:**

The coefficient of BMI is -0.453, and the p-value is 0.21. There is little evidence showing a strong relation ship between BMI and Estradiol level.



2. Relationship between BMI and serum estradiol change after controlling for all the other risk factors

```{r estradl_reg}
estradl_reg = 
  estradl_df %>% 
  lm(estradl ~ .-id, data = .)

estradl_reg %>% broom::tidy() %>% knitr::kable(digits = 3) 
```

**Comments:**

The coefficient of BMI after controlling for all the other risk factors changed from -0.453 to -0.107, and the p-value changed from 0.21 to 0.774 The relationship between BMI and Estradiol level seems to be more insignificant after controlling.

The p-value of `entage`, `nunchild`,`agemenar` and `bmi` are relatively high and there coefficient is small in magnitude, which implies there might not be a strong relationship between estradiol level. However, the p-value of `ethnicCaucasian` is small, and its coefficient is large in magnitude, there might be a relationship between ethnic and estradiol level.

        


3. Focus on BMI, ethnic and estradiol level

a) Graphical displays and numerical summaries

First I will draw a scatter plot about Estradiol level vs BMI by Ethnic:

```{r ethn_bmi_plt}
estradl_df %>% 
  ggplot(aes(x = bmi, y = estradl, color = ethnic))+
  geom_point() +
  stat_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Scatterplot of Estradiol level vs BMI by Ethnic",
    x = "BMI",
    y = "Estradiol level"
  )
```

From the plots, we can see a cross over two regression line, that is a indication of interactions between `BMI` and `ethnic`.

Let's build a model with this interaction and see if it is significant.


```{r interaction_reg}
interaction_reg = 
  lm(estradl ~ bmi * ethnic, data = estradl_df)

summary(interaction_reg)
```

From the summary of the model, we can see that the interaction is significant. With p-value 0.0133.


b) Additional steps

Since there is a significant interaction, we need to do stratified analysis.

```{r stratified_df, echo = T}
caucasian_df = 
  estradl_df %>% 
  filter(ethnic == "Caucasian")

aamerican_df = 
  estradl_df %>% 
  filter(ethnic == "African American")

strat_reg_cau = lm(estradl ~ bmi, data = caucasian_df)
strat_reg_aam = lm(estradl ~ bmi, data = aamerican_df)
```

So in Caucasian, a negative, relatively large in magnitude association b/w BMI and estradiol level

```{r cau_reg}
summary(strat_reg_cau)
```


And in African American, a positive association b/w BMI and estradiol level.


```{r aam_reg}
summary(strat_reg_aam)
```

However, both associations are not statistically significant.

And to see if Ethnic is a confounder of BMI, it need to meet 3 conditions

Condition 1) Associated with the outcome:
```{r confonder_1}
conf_1_reg = 
  estradl_df %>% 
  lm(estradl ~ ethnic, data = .)

summary(conf_1_reg)
```

Yes, ethnic is associated with estradiol level with a very small p-value.


Condition 2) Associated with the exposure:
```{r confonder_2}
conf_2_reg = 
  estradl_df %>% 
  lm(bmi ~ ethnic, data = .)


summary(conf_2_reg)
```

Yes, ethnic is associated with BMI with a extreme small p-value.

Condition 3) Not on the causal pathway b/w exposure and outcome, which is obvious.

```{r control_reg}
control_reg = 
  estradl_df %>% 
  lm(estradl~ bmi + ethnic, data = .)

bmi_reg %>% broom::tidy() %>% knitr::kable()
control_reg %>% broom::tidy() %>% knitr::kable()
```

And by comparing model controlling `ethnic` and not, we can see that the BMI coefficient reduced from -0.453 in SLR to -0.041 in MLR after adjusting for `ethnic` (~90% reduction). We can conclude that `ethnic` confounds the relationship b/w `BMI` and `estradiol level`.

```{r boxplot_end}
estradl_df %>% 
  ggplot(aes(x = ethnic, y = estradl))+
  geom_boxplot() + 
  geom_point(aes(x = ethnic, y = mean(estradl)), color = "red") +
  labs(
    title = "Distribution of Estradiol level by Ethnic",
    y = "Estradiol level",
    x = "Ethnic"
  )

```

