---
title: "p8130_hw6_rw2844"
author: "Renjie Wei"
date: "11/30/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(cowplot)
library(patchwork)
library(modelr)
knitr::opts_chunk$set(
  echo = F,
  out.width = "100%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(2844)
```

# Problem 1


1. Create a correlation matrix

```{r read_patsatisfaction}
patsat_df = 
  read_csv("./data/PatSatisfaction.csv") %>% janitor::clean_names() %>% mutate(satisfaction = safisfaction) %>% select(satisfaction, everything(),-safisfaction)

patsat_df %>% cor() %>% corrplot::corrplot(type = "upper", order = "hclust", tl.col = "black", tl.srt = 45)
```

It seems that each predictor has a negative correlation with the outcome of interest.




2. Fit a multiple regression model.

```{r patsat_reg}
patsat_reg =
  lm(satisfaction ~ age + severity + anxiety, data = patsat_df)

null_reg = 
  lm(satisfaction ~ 1, data = patsat_df)
```



Let's set up the test hypotheses:

$H_0~:~\beta_i = 0,~i = 1,2,3$ 

$H_1 : at~least~one~of~the~coefficient~is~not~equal~to~0$

And our model to be test is:
$$Model_{test}:~Statisfaction=`r str_c(patsat_reg$coefficients %>% round(2),c("",patsat_reg$terms %>% attr("term.labels")),sep=" ") %>% paste(collapse = "")`$$

We can test this model against the model only with intercept:

$$Model_{null}:~Statisfaction=`r str_c(null_reg$coefficients %>% round(2),c("",null_reg$terms %>% attr("term.labels")),sep=" ") %>% paste(collapse = "")`$$

And we do the ANOVA test:

The F statistic is calculated by:
$$F_{stat} = \frac{MSR}{MSE} \sim F_{p,~n-p-1},~where~p=3,~n=46$$
```{r patsat_anova}
anova(null_reg, patsat_reg)
```

**Decision Rules:**
$Reject ~ H_0 ~ if ~ F_{stat}>F_{1-\alpha;~p,~n-p-1}$

In our situation, $F_{stat} = 30.1>F_{0.95;~3,~42}=`r qf(0.95,3,42)`$

So, we reject the null hypothesis with 95% confidence and conclude that at least one coefficient is not equal to zero.




3. Show the regression results for all estimated slope coefficients with 95% CIs.

```{r patsat_ci}
patsat_ci = 
  tibble(
    broom::tidy(patsat_reg),
    as_tibble(confint(patsat_reg))
  ) %>% 
  select(term, estimate, "2.5 %", "97.5 %")

patsat_ci %>% 
  knitr::kable(digits = 3)
```

**Interpretation:**

The 95% CI for severity of illness is $(-1.435,~0.551)$, that means at 95% confidence level, the mean 
change of patient satisfaction given all the same except for severity of illness per unit is between $(-1.435,~0.551)$, noticing that 0 is in this interval.




4. Obtain an interval estimate for a new patient’s satisfaction with Age=35, Severity=42, and Anxiety=2.1.

The 95% PI for this new patient is :
```{r patsat_int_est}
predict(
  patsat_reg,
  tibble(age=35, severity=42, anxiety=2.1),
  interval = "prediction"
  ) %>% 
  as_tibble() %>% 
  select(lwr,upr) %>% 
  knitr::kable(digits = 3)
```

**Interpretation:**

This means at 95% confidence level, the true estimate of patient satisfaction is between $(50.062, 93.304)$.




5. 
  a) Test whether ‘anxiety level’ can be dropped from the regression model, given the other two covariates are retained.
  
  